The Talking Heads Experiment

### 2015-04-10 chap9/chap9.tex
cumulative update, mainly for Ch. 7-12

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.75\textwidth]{chap9/figs/cambridge-view.jpg}}
\caption{\label{fig:sideview} 
View through the street window inside the Kettle's Yard gallery in Cambridge. The cameras are located before 
the towers. The geometric figures are attached to the wall and explanations of the experiment are located on the right.}
\end{figure}

The N01SE exhibition was curated by Adam Lowe (see \figref{fig:lowe}) and Simon Schaffer. 
Adam Lowe is an artist and technologist. He is currently the director of Factum arte (Madrid) which is specialised 
in making life-like replicas of paintings, sculptures and archeological objects, using laser-scanners and 3d printers. 
Recent realisations include the sculptures of Giambattista Piranesi \citep{Lowe:2010}, the 
paintings of Caravaggio and the tomb of Tutankhamun. 
Simon Schaffer is a science historian, professor at the University of Cambridge at the department of History and Philosophy 
of Science. He wrote extensively about the historical developments in scientific research \citep{Schaffer:2011}
and animated television and radio programs, including {\itshape Light Fantastic} (BBC4). 
\begin{figure}[htbp]
  \centerline{\includegraphics[width=.70\textwidth]{chap9/figs/lowe.pdf}}
\caption{\label{fig:lowe} 
Adam Lowe (curator of N01SE) during installation of the Talking Heads experiment at the Wellcome Gallery in London. 
The backwall contained the figures. On the right wall, posters were displayed explaining the experiment.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.60\textwidth]{chap9/figs/NOISE-programmaboek.jpg}}
\caption{\label{fig:program} 
Catalogue cover and poster of the N01SE exhibition at the Wellcome Gallery in London.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.55\textwidth]{chap9/figs/london-heads.pdf} 
\includegraphics[width=.44\textwidth]{chap9/figs/screen.pdf}}
\caption{\label{fig:london-heads} 
Installation at the Wellcome Gallery in London. Left: Talking Heads cameras oriented towards the wall on which 
geometric figures were pasted. Right: Projection of interaction during ongoing experiment. A game just failed and 
the speaker says ``no''.} 
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.65\textwidth]{chap9/figs/th4.jpg}}
\caption{\label{fig:palais} 
Talking Heads installation at the Palais de la D\'{e}couverte. It featured new fancy structures that 
made the installation more attractive visually. Daily explanations were given to visitors 
by the staff of the Palais de la D\'{e}couverte.} 
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.60\textwidth]{chap9/figs/road.pdf}}
\caption{\label{fig:road} 
Portable installation with two pan-tilt cameras and a portable computer that was able to run the TH software.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.90\textwidth]{chap9/figs/Lausanne.pdf}}
\caption{\label{fig:lausanne} 
Live installation and demonstration of the Talking Heads experiment at the European Conference on Artificial 
Life in 1999.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.80\textwidth]{chap9/figs/mich-gallery.pdf}}
\caption{\label{fig:mich} 
Live installation at the gallery of Ludo Mich in Antwerp. There was no white board but different 
small pancartes with possible scenes (see in the middle of the picture). The game was displayed much larger against
the back wall.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.95\textwidth]{chap9/figs/look-into-box.pdf}}
\caption{\label{fig:lookintobox} 
Look into the Box installation at the Paris Museum of Modern Art. Left: Box with camera inside. A lens would make 
the eye look bigger for the camera. Right: Projection of the eye on a big screen.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.30\textwidth]{chap9/figs/eyes.pdf}
\includegraphics[width=.30\textwidth]{chap9/figs/identified-colors.pdf}}
\caption{\label{fig:eyes} 
Example interaction of the ``Look into the Box" art piece. 
Left: Top and pixilated eye of a spectator. Right: the main colours that 
were extracted from this image. Agents played language games to describe these eye colours.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.65\textwidth]{chap9/figs/ital-talk.pdf}
\includegraphics[width=.30\textwidth]{chap9/figs/ital2.pdf}}
\caption{\label{fig:spoleto} 
Left: My presentation at the Spoleto Science Festival. Right: Nicolas Neubauer debugging 
the Look into the Box installation.
 }
\end{figure}

The Look into the Box installation was also shown during the ``Intensive Science" exhibitions organised in October 
2006 on the occasion of the 10th anniversary of the Sony Computer Science Laboratory.\is{Intensive Science exhibition}
It was first shown in Paris at 
the exhibition space ``La Maison Rouge" near the Bastille in Paris, which featured science/art installations 
and collaborations involving members of the Sony Computer Science Laboratory, including work by Atau Tanaka, 
Francois Pachet in collaboration with Jazz pianist Albert van Veendaal, Peter Hanappe in collaboration with 
photographer Armin Linke, Frederic Kaplan in collaboration with the Design School of EPFL in Lausanne. 
The same exhibition traveled to Tokyo where it was shown in the Sony Explorascience museum from 22 December 2006 
to 12 February 2007 (see \figref{fig:intensive-science}). 
\begin{figure}[htbp]
  \centerline{\includegraphics[width=.80\textwidth]{chap9/figs/explorascience.pdf}}
\caption{\label{fig:intensive-science} 
Installation at the Tokyo Explorascience Museum. The box is in the left corner. The eye is projected on a 
big screen. A smaller screen shows the image captured by the camera, the colours recognised, and the words used by 
the agents.}
\end{figure}
\section{Conclusions}

>>>>

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.75\textwidth]{chap9/figs/cambridge-view.jpg}}
\caption{\label{fig:sideview}View through the street window inside the Kettle's Yard gallery in Cambridge. The cameras are located before 
the towers. The geometric figures are attached to the wall and explanations of the experiment are located on the right.}
\end{figure}

The N01SE exhibition was curated by Adam Lowe (see \figref{fig:lowe}) and Simon Schaffer. 
Adam Lowe is an artist and technologist. He is currently the director of Factum arte (Madrid) which is specialised 
in making life-like replicas of paintings, sculptures and archeological objects, using laser-scanners and 3d printers. 
Recent realisations include the sculptures of Giambattista Piranesi \citep{Lowe:2010}, the 
paintings of Caravaggio and the tomb of Tutankhamun. 
Simon Schaffer is a science historian, professor at the University of Cambridge at the department of History and Philosophy 
of Science. He wrote extensively about the historical developments in scientific research \citep{Schaffer:2011}
and animated television and radio programs, including {\itshape Light Fantastic} (BBC4). 
\begin{figure}[htbp]
  \centerline{\includegraphics[width=.70\textwidth]{chap9/figs/lowe.pdf}}
\caption{\label{fig:lowe}Adam Lowe (curator of N01SE) during installation of the Talking Heads experiment at the Wellcome Gallery in London. 
The backwall contained the figures. On the right wall, posters were displayed explaining the experiment.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.60\textwidth]{chap9/figs/NOISE-programmaboek.jpg}}
\caption{\label{fig:program}Catalogue cover and poster of the N01SE exhibition at the Wellcome Gallery in London.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.55\textwidth]{chap9/figs/london-heads.pdf} 
\includegraphics[width=.44\textwidth]{chap9/figs/screen.pdf}}
\caption{\label{fig:london-heads}Installation at the Wellcome Gallery in London. Left: Talking Heads cameras oriented towards the wall on which 
geometric figures were pasted. Right: Projection of interaction during ongoing experiment. A game just failed and 
the speaker says ``no''.} 
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.65\textwidth]{chap9/figs/th4.jpg}}
\caption{\label{fig:palais}Talking Heads installation at the Palais de la D\'{e}couverte. It featured new fancy structures that 
made the installation more attractive visually. Daily explanations were given to visitors 
by the staff of the Palais de la D\'{e}couverte.} 
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.60\textwidth]{chap9/figs/road.pdf}}
\caption{\label{fig:road}Portable installation with two pan-tilt cameras and a portable computer that was able to run the TH software.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.90\textwidth]{chap9/figs/Lausanne.pdf}}
\caption{\label{fig:lausanne}Live installation and demonstration of the Talking Heads experiment at the European Conference on Artificial 
Life in 1999.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.80\textwidth]{chap9/figs/mich-gallery.pdf}}
\caption{\label{fig:mich}Live installation at the gallery of Ludo Mich in Antwerp. There was no white board but different 
small pancartes with possible scenes (see in the middle of the picture). The game was displayed much larger against
the back wall.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.95\textwidth]{chap9/figs/look-into-box.pdf}}
\caption{\label{fig:lookintobox}Look into the Box installation at the Paris Museum of Modern Art. Left: Box with camera inside. A lens would make 
the eye look bigger for the camera. Right: Projection of the eye on a big screen.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.30\textwidth]{chap9/figs/eyes.pdf}
\includegraphics[width=.30\textwidth]{chap9/figs/identified-colors.pdf}}
\caption{\label{fig:eyes}Example interaction of the ``Look into the Box" art piece. 
Left: Top and pixilated eye of a spectator. Right: the main colours that 
were extracted from this image. Agents played language games to describe these eye colours.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.65\textwidth]{chap9/figs/ital-talk.pdf}
\includegraphics[width=.30\textwidth]{chap9/figs/ital2.pdf}}
\caption{\label{fig:spoleto}Left: My presentation at the Spoleto Science Festival. Right: Nicolas Neubauer debugging 
the Look into the Box installation.
 }
\end{figure}

The Look into the Box installation was also shown during the ``Intensive Science" exhibitions organised in October 
2006 on the occasion of the 10th anniversary of the Sony Computer Science Laboratory.\is{Intensive Science exhibition}
It was first shown in Paris at 
the exhibition space ``La Maison Rouge" near the Bastille in Paris, which featured science/art installations 
and collaborations involving members of the Sony Computer Science Laboratory, including work by Atau Tanaka, 
Francois Pachet in collaboration with Jazz pianist Albert van Veendaal, Peter Hanappe in collaboration with 
photographer Armin Linke, Frederic Kaplan in collaboration with the Design School of EPFL in Lausanne. 
The same exhibition traveled to Tokyo where it was shown in the Sony Explorascience museum from 22 December 2006 
to 12 February 2007 (see \figref{fig:intensive-science}). 
\begin{figure}[htbp]
  \centerline{\includegraphics[width=.80\textwidth]{chap9/figs/explorascience.pdf}}
\caption{\label{fig:intensive-science}Installation at the Tokyo Explorascience Museum. The box is in the left corner. The eye is projected on a 
big screen. A smaller screen shows the image captured by the camera, the colours recognised, and the words used by 
the agents.}
\end{figure}
\section{Conclusions}
